A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-15 6_validation.tex
describe dataset

\section{Validation}
In order to test our framework we have assembled a data set of various types of 3D model, ranging over various applications and various types of geometry.
The dataset is described in detail in the accompanying data in \cref{dataset}.
We sliced all models in the data set and selected 300 random slices from the total set of slices.

\todo{describe dataset of 3d models and random slices... X number of 3d files. varying in size, topology, features (size). random selection of slices. 300 slices total.  5 toolpath strategies were applied for each layer.}

@@

>>>>

\section{Validation}
In order to test our framework we have assembled a data set of various types of 3D model, ranging over various applications and various types of geometry.
The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the dataset and selected 300 random slices from the total set of slices.

@@

We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.
